Environments and eval in R

### 2021-04-06 analysis/environments.Rmd
Correct src ref numbers

if(params$force_rebuild || rebuild) {
  read_fst(calls_path) %>% as_tibble() -> E_raw

@@

```{r envir_most_common}
frequent_envir <- E_envir %>% group_by(src_ref) %>% 
  summarize(n_envir = n_distinct(envir), envir = paste0(unique(envir), collapse = " ; "), envir_type = paste0(unique(envir_type), collapse = " ; "))

#stopifnot(frequent_envir$n_envir <= 1)
```

@@

@@

>>>>

if(params$force_rebuild || rebuild) {
  read_fst(calls_path) %>% as_tibble() %>% semi_join(C_raw, by = c("eval_source" = "package")) -> E_raw

@@

```{r envir_most_common}
frequent_envir <- E_envir %>% group_by(src_ref) %>% 
  summarize(n_envir = n_distinct(envir), envir = paste0(unique(envir), collapse = " ; "), envir_type = paste0(unique(envir_type), collapse = " ; "), n_types = n_distinct(envir_type))

#stopifnot(frequent_envir$n_envir <= 1)
# 2 sites have 2 envir...
```

@@

# TODO: handle scientific notation for caller-1e+00-

@@

# Better-looking env class

`caller-n` wins over any specific env. We add `+` if there are any `new`.

```{r}
env_calls <- env_calls %>%
  mutate(env_class = if_else(environment_class == "loop", "loop", paste0(if_else(is.na(hierarchy), specific_env, as.character(hierarchy)), if_else(is.na(new_env), "", "+"))))
```
